---
title: "R Notebook"
output: pdf_document
---
### Import Libraries

```{r}
library(tidyverse)
library(ggplot2)
library(psych)
library(dplyr)
```

### Load our Data

```{r}
data <- read.csv("assets/StudentsPerformance.csv")
data%>%head()
ndata<-mutate(data,mean=(`math.score`+`reading.score`+`writing.score`)/3) #mean of three score
table(data$parental.level.of.education)
table(data$lunch)
```

### Comparing the Reading and Writing Scores again Math Scores

```{r}
girl_data<-data%>%filter(gender=='female')
boy_data<-data%>%filter(gender=='male')
ggplot()+
  geom_point(girl_data,mapping=aes(`math.score`,`reading.score`,color='female'))+
  geom_point(boy_data,mapping=aes(`math.score`,`reading.score`,color='male'))+labs(title='Math and Reading score')
ggplot()+
  geom_point(girl_data,mapping=aes(`math.score`,`writing.score`,color='female'))+
  geom_point(boy_data,mapping = aes(`math.score`,`writing.score`,color='male'))+labs(title='Math and Writing score')
```
Now we comparing Reading and Writing Scores

```{r}
ggplot()+
  geom_point(girl_data,mapping=aes(`reading.score`,`writing.score`,color='female'),alpha=1/2)+
  geom_point(boy_data,mapping = aes(`reading.score`,`writing.score`,color='male'),alpha=1/2)+labs(title='Reading and Writing')
```

```{r}
pairs.panels(data[6:8])
```

The plot above shows that females have a higher reading/wriitng score and males tend to have higher math scores

### Averages Scores of Each Group

```{r}
ndata%>%
group_by(race.ethnicity)%>%
summarize(avg_score=round(sum(mean)/n(),1))%>%
ggplot(aes(race.ethnicity,avg_score,fill=race.ethnicity))+geom_bar(stat='identity')+
geom_text(aes(label = avg_score))+coord_flip()+labs(title='Average score of each group')+guides(fill=F)

```

### Level of Education of Parents

```{r}
data%>%group_by(race.ethnicity,parental.level.of.education)%>%summarize(count=n())%>%
ggplot()+geom_col(aes(race.ethnicity,count,fill=parental.level.of.education),position='dodge')+scale_fill_manual(values = c("#4B0082", "#800080","#9932CC","#6A5ACD","#BA55D3","#EE82EE"))
```

### Education of Parents and Mean Score

```{r}
groupa<-ndata%>%filter(`race.ethnicity`=='group A')
groupb<-ndata%>%filter(`race.ethnicity`=='group B')
groupc<-ndata%>%filter(`race.ethnicity`=='group C')
groupd<-ndata%>%filter(`race.ethnicity`=='group D')
groupe<-ndata%>%filter(`race.ethnicity`=='group E')
ggplot(groupa)+geom_boxplot(mapping=aes(x=reorder(`parental.level.of.education`,mean,median),mean))+
  ggtitle('GROUP A')+xlab('parental level of education')+coord_flip()
ggplot(groupb)+geom_boxplot(mapping=aes(x=reorder(`parental.level.of.education`,mean,median),mean))+
  ggtitle('GROUP B')+xlab('parental level of education')+coord_flip()
ggplot(groupc)+geom_boxplot(mapping=aes(x=reorder(`parental.level.of.education`,mean,median),mean))+
  ggtitle('GROUP C')+xlab('parental level of education')+coord_flip()
ggplot(groupd)+geom_boxplot(mapping=aes(x=reorder(`parental.level.of.education`,mean,median),mean))+
  ggtitle('GROUP D')+xlab('parental level of education')+coord_flip()
ggplot(groupe)+geom_boxplot(mapping=aes(x=reorder(`parental.level.of.education`,mean,median),mean))+
  ggtitle('GROUP E')+xlab('parental level of education')+coord_flip()
```

### Mean Score of Each Plot

```{r}
ggplot()+geom_freqpoly(groupa,mapping=aes(mean,color='A'))+geom_freqpoly(groupb,mapping=aes(mean,color='B'))+
  geom_freqpoly(groupc,mapping=aes(mean,color='C'))+geom_freqpoly(groupd,mapping=aes(mean,color='D'))+
  geom_freqpoly(groupe,mapping=aes(mean,color='E'))
```

```{r}
group_A<-groupa%>%rename(mean_A=mean)%>%select(mean_A)%>%arrange(desc(`mean_A`))%>%head(89)%>%round(digits = 1)
group_B<-groupb%>%rename(mean_B=mean)%>%select(mean_B)%>%arrange(desc(`mean_B`))%>%head(89)%>%round(digits = 1)
group_C<-groupc%>%rename(mean_C=mean)%>%select(mean_C)%>%arrange(desc(`mean_C`))%>%head(89)%>%round(digits = 1)
group_D<-groupd%>%rename(mean_D=mean)%>%select(mean_D)%>%arrange(desc(`mean_D`))%>%head(89)%>%round(digits = 1)
group_E<-groupe%>%rename(mean_E=mean)%>%select(mean_E)%>%arrange(desc(`mean_E`))%>%head(89)%>%round(digits = 1)
cbi<-cbind(group_A,group_B,group_C,group_D,group_E)
cbi%>%head()
summary(cbi)
```

Students who completed test prep courses have higher mean scores

```{r}
#(3)observe test preparation course and mean
uncomplete_prep<-ndata%>%filter(`test.preparation.course`=='none')
complete_prep<-ndata%>%filter(`test.preparation.course`=='completed')
prep1<-ggplot()+geom_bar(uncomplete_prep,mapping = aes(x=mean,fill='uncompleted'))+
  geom_bar(complete_prep,mapping=aes(x=mean,fill='comploeted'))
prep2<-ggplot()+geom_boxplot(ndata,mapping=aes(`test.preparation.course`,mean))
prep1
prep2
```

